Changelog

### 2021-05-25 changelog.tex
Updates from Overleaf

It is hard to understand Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name. \textbf{In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.}''

@@

d. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they have different threat models.
\item \textbf{iid assumption – does it fit your research on side-channel?}

>>>>

It is hard to explain Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name. In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.''

@@

b. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they have different threat models.
\item \textbf{iid assumption – does it fit your research on side-channel?}
